\chapter{Design Reviews \& Meetings}
Make sure to reference the videos.

\section{Design Review 1}

\subsection{Questions \& Sugguestions}
\begin{itemize}
\item How to understand space and time and have a sense of space and time?
\item Using some images of space and time can bring people closer to understand them.
\item Math is the major barrier for most people to understand the complexity of the space and time.
\item Astronomy in popular culture, like space travel
\item How to convert the lensing to people?
\item How to attract people to play with the stuff?
\item Make something more tangible, such as a basketball.
\item Constellations, in a game show.
\item Google Earth
\item Visualize things beyond our scale, like microscope.
\item Exposite more about lensing, make it simpler to understand.
\item Start from small scale to big scale.
\item It is easy for people to forget these things. How to keep them remembering these?
\item The speed of light, faraway object we see are actually many years ago. How to make people understand this better?
\item The fate of life and our civilizations.
\end{itemize}

\section{Design Review 2}

\subsection{Questions \& Sugguestions}
\begin{itemize}
\item Using voice to tune the star evolution
\item Using heart beat to regulate star oscillation
\item How to balance technology and principles? Too much Tech. stuff, are they better suited for presenting th central idea?
\item Place the multi-touch table into a separate place so that to have a sense of reality. 
\end{itemize}

\section{Other Input}

